Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2014-10-01 exp1/present2013.tex
take out the experiment description
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@768 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{block}{Description}
  Experiment with 8 factors, 2 levels where we compare a single SPARQL
  implementation before and after some change. We used \texttt{4store}
  where we insert \textsf{sleep} statements in the join function on
  one level and language matching function on the other, to simulate
  an optimization that may have detrimental side-effects.

\end{block}

@@

>>>>

@@

  \begin{itemize}
  \item Experiment with 8 factors, 2 levels
  \item sleep to simulate an optimization that may have detrimental
    side-effects
  \end{itemize}
